Native advertising as a content marketing strategy

### 2024-08-26 analysis/paper/paper.tex
los

@@

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{library}\NormalTok{(dplyr)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## Warning: package 'dplyr' was built under R version 4.3.3
\end{verbatim}

\begin{verbatim}
## 
## Attaching package: 'dplyr'
\end{verbatim}

\begin{verbatim}
## The following objects are masked from 'package:stats':
## 
##     filter, lag
\end{verbatim}

\begin{verbatim}
## The following objects are masked from 'package:base':
## 
##     intersect, setdiff, setequal, union
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{library}\NormalTok{(readr)}
\FunctionTok{library}\NormalTok{(ggplot2)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## Warning: package 'ggplot2' was built under R version 4.3.3
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{library}\NormalTok{(ggthemes)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## Warning: package 'ggthemes' was built under R version 4.3.3
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{library}\NormalTok{(tidyverse)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## -- Attaching core tidyverse packages ------------------------ tidyverse 2.0.0 --
## v forcats   1.0.0     v stringr   1.5.1
## v lubridate 1.9.3     v tibble    3.2.1
## v purrr     1.0.2     v tidyr     1.3.0
\end{verbatim}

\begin{verbatim}
## -- Conflicts ------------------------------------------ tidyverse_conflicts() --
## x dplyr::filter() masks stats::filter()
## x dplyr::lag()    masks stats::lag()
## i Use the conflicted package (<http://conflicted.r-lib.org/>) to force all conflicts to become errors
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{library}\NormalTok{(readxl)}
\FunctionTok{library}\NormalTok{(xlsx)}
\FunctionTok{library}\NormalTok{(here)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## Warning: package 'here' was built under R version 4.3.3
\end{verbatim}

\begin{verbatim}
## here() starts at C:/Users/lukas/Dropbox/Članci/NativeAdvertising
\end{verbatim}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{original }\OtherTok{\textless{}{-}} \FunctionTok{read.xlsx}\NormalTok{(}\FunctionTok{here}\NormalTok{(}\StringTok{"analysis"}\NormalTok{, }\StringTok{"data"}\NormalTok{, }\StringTok{"raw\_data"}\NormalTok{, }\StringTok{"native\_articles.xlsx"}\NormalTok{), }\AttributeTok{sheetIndex =} \DecValTok{1}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{mutate}\NormalTok{(}\AttributeTok{V1 =} \FunctionTok{as.numeric}\NormalTok{(V1))}
\NormalTok{variables }\OtherTok{\textless{}{-}} \FunctionTok{read.xlsx}\NormalTok{(}\FunctionTok{here}\NormalTok{(}\StringTok{"analysis"}\NormalTok{, }\StringTok{"data"}\NormalTok{, }\StringTok{"raw\_data"}\NormalTok{, }\StringTok{"native\_research.xlsx"}\NormalTok{), }\AttributeTok{sheetIndex =} \DecValTok{1}\NormalTok{)}

\NormalTok{dta }\OtherTok{\textless{}{-}} \FunctionTok{merge}\NormalTok{(}
\NormalTok{  original }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{filter}\NormalTok{(V1 }\SpecialCharTok{\%in\%}\NormalTok{ variables}\SpecialCharTok{$}\NormalTok{V1),}
\NormalTok{  variables }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{select}\NormalTok{(}\SpecialCharTok{{-}}\FunctionTok{c}\NormalTok{(}\DecValTok{23}\NormalTok{, }\DecValTok{24}\NormalTok{, }\DecValTok{25}\NormalTok{)),}
  \AttributeTok{by =} \StringTok{"V1"}\NormalTok{,}
  \AttributeTok{all.x =} \ConstantTok{TRUE}
\NormalTok{)}

>>>>

\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}

@@

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{library}\NormalTok{(dplyr)}
\FunctionTok{library}\NormalTok{(readr)}
\FunctionTok{library}\NormalTok{(ggplot2)}
\FunctionTok{library}\NormalTok{(ggthemes)}
\FunctionTok{library}\NormalTok{(tidyverse)}
\FunctionTok{library}\NormalTok{(readxl)}
\FunctionTok{library}\NormalTok{(xlsx)}
\FunctionTok{library}\NormalTok{(here)}
\FunctionTok{library}\NormalTok{(knitr)}
\CommentTok{\#library(htmltools)}
\FunctionTok{library}\NormalTok{(kableExtra)}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{original }\OtherTok{\textless{}{-}} \FunctionTok{read.xlsx}\NormalTok{(}\FunctionTok{here}\NormalTok{(}\StringTok{"analysis"}\NormalTok{, }\StringTok{"data"}\NormalTok{, }\StringTok{"raw\_data"}\NormalTok{, }\StringTok{"native\_articles.xlsx"}\NormalTok{), }\AttributeTok{sheetIndex =} \DecValTok{1}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{mutate}\NormalTok{(}\AttributeTok{V1 =} \FunctionTok{as.numeric}\NormalTok{(V1))}

\NormalTok{variables }\OtherTok{\textless{}{-}} \FunctionTok{read.xlsx}\NormalTok{(}\FunctionTok{here}\NormalTok{(}\StringTok{"analysis"}\NormalTok{, }\StringTok{"data"}\NormalTok{, }\StringTok{"raw\_data"}\NormalTok{, }\StringTok{"native\_research.xlsx"}\NormalTok{), }\AttributeTok{sheetIndex =} \DecValTok{1}\NormalTok{)}

\NormalTok{dta }\OtherTok{\textless{}{-}} \FunctionTok{merge}\NormalTok{(original }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{filter}\NormalTok{(V1 }\SpecialCharTok{\%in\%}\NormalTok{ variables}\SpecialCharTok{$}\NormalTok{V1),}
\NormalTok{  variables }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{select}\NormalTok{(}\SpecialCharTok{{-}}\FunctionTok{c}\NormalTok{(}\DecValTok{23}\NormalTok{, }\DecValTok{24}\NormalTok{, }\DecValTok{25}\NormalTok{)),}
  \AttributeTok{by =} \StringTok{"V1"}\NormalTok{,}
  \AttributeTok{all.x =} \ConstantTok{TRUE}\NormalTok{)}
